Results

### 2025-06-09 notebooks/00_index.qmd
fig: update overplot

```{julia}
tvars_wind = [
    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel),
    set(Wind.n; ylabel=n_ylabel),
    # set(Wind.V_GSE_p; ylabel=V_ylabel),
    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel),
    set(Wind.T; ylabel=T_ylabel)
]
```

```{julia}
using GLMakie
```

```{julia}
using Intervals: Interval
thx_v_gse = THEMIS.V_GSE(tmin_wind, tmax_wind)
_times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
dt = Minute(10)
its = union([Interval(t - dt, t + dt) for t in _times])
_tmask! = tmask!(its)
```

```{julia}
tvars_themis = [
    set(_tmask! ∘ tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    THEMIS.n,
    _tmask! ∘ THEMIS.V_GSE,
    set(_tmask! ∘ THEMIS.eTemp; ylabel=T_ylabel)
]

@@

```{julia}
tmin_psp = "2021-01-14"
tmax_psp = "2021-01-20"

f = Figure(; size=(900, 600))
legend = (; position=Top())
labels = '1':'9'
# plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
# add_labels!(f[1, 1]; labels, open="(a.")

# tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
# add_labels!(f[1, 2]; labels, open="(b.")

tplot(f[1, 3], tvars_themis, tmin_wind, tmax_wind; legend)
add_labels!(f[1, 3]; labels, open="(c.")
f
# easy_save("overview")
```

>>>>

```{julia}
tvars_wind = [
    set(tnorm_combine ∘ Wind.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    set(Wind.n; ylabel=n_ylabel),
    # set(Wind.V_GSE_p; ylabel=V_ylabel),
    replace_outliers! ∘ set(Wind.V_GSE_K0; ylabel=V_ylabel, labels=V_XYZ_labels),
    set(Wind.T; ylabel=T_ylabel)
]
```

```{julia}
using CairoMakie
CairoMakie.activate!()
```

```{julia}
using Intervals: Interval

function get_themis_tmask(t0, t1) 
    thx_v_gse = THEMIS.V_GSE(t0, t1)
    _times = @views SPEDAS.times(thx_v_gse)[(thx_v_gse[:, 1].>-200u"km/s").|(thx_v_gse[:, 2].<-50u"km/s")]
    dt = Minute(10)
    its = union([Interval(t - dt, t + dt) for t in _times])
    return tmask!(its)
end
```

```{julia}
tvars_themis = [
    set(tnorm_combine ∘ THEMIS.B_GSE; ylabel=B_ylabel, labels=B_XYZ_labels),
    set(THEMIS.n; ylabel=n_ylabel),
    replace_outliers! ∘ set(THEMIS.V_GSE; ylabel=V_ylabel, labels=V_XYZ_labels),
    set(THEMIS.eTemp; ylabel=T_ylabel)
]

@@

```{julia}
for enc in (7, 8, 9)
    (tmin_psp, tmax_psp), (tmin_wind, tmax_wind) = get_timerange(enc)

    _tmask! = get_themis_tmask(tmin_wind, tmax_wind)

    legend = (; position=Top())
    labels = '1':'9'

    f = Figure(; size=(1200, 600))
    plots = tplot(f[1, 1], tvars_psp[1:3], tmin_psp, tmax_psp; legend)
    add_labels!(f[1, 1]; labels, open="(a.")
    tplot(f[1, 2], tvars_wind[1:3], tmin_wind, tmax_wind; legend)
    add_labels!(f[1, 2]; labels, open="(b.")
    tplot(f[1, 3], _tmask! .∘ tvars_themis[1:3], tmin_wind, tmax_wind; legend)
    add_labels!(f[1, 3]; labels, open="(c.")
    easy_save("overview-$enc")

    f = Figure(; size=(1200, 600))
    plots = tplot(f[1, 1], tvars_psp, tmin_psp, tmax_psp; legend)
    add_labels!(f[1, 1]; labels, open="(a.")
    tplot(f[1, 2], tvars_wind, tmin_wind, tmax_wind; legend)
    add_labels!(f[1, 2]; labels, open="(b.")
    tplot(f[1, 3], _tmask! .∘ tvars_themis, tmin_wind, tmax_wind; legend)
    add_labels!(f[1, 3]; labels, open="(c.")
    easy_save("overview-$enc-all")
end
```
